Efficient Handling of String-Number Conversion

### 2019-11-22 draft.tex
Update draft.tex

\begin{abstract}
String-number conversion is an important class of constraint needed for the symbolic execution for programs. It is particular important in the analysis of scripting languages such as JavaScript and Python, where string-number conversion is a part of the definition of the core semantics of the language. However, the state-of-the-art constraint solvers have only very limited support to this type of constraint. In this paper, we propose an approach that can support a combination of string-number conversion as well as other common types of string constraints efficiently. Experimental results show that it significantly outperforms other state-of-the-art tools on benchmarks that involves string-number conversion.
\end{abstract}
 \setcopyright{none} 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{document}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\newcommand{\hide}[1]{}
\newcommand{\tool}{{\textsf{Z3-PFA}}}
\newcommand{\dr}{\mathcal{R}}
\newcommand{\nat}{\mathbb{N}}
\newcommand{\integers}{\mathbb{Z}}
\newcommand{\todo}[1]{{\color{blue}TODO: #1}}
\newcommand{\lh}[1]{{\color{orange}Lukas: #1}}
\newcommand{\changed}[1]{{\color{orange}#1}}
\newcommand{\yfc}[1]{{\color{blue}YFC: #1}}
\newcommand{\petr}[1]{{\color{pink}Petr: #1}}
\newcommand{\chatAt}[2]{\mbox{\textsf{charAt}($#1$, $#2$)}}
\newcommand{\ite}[3]{\mbox{\textsf{ite}($#1$, $#2$, $#3$)}}
\newcommand{\sti}[1]{\mbox{\textsf{toNum}($#1$)}}
\newcommand{\its}[1]{\mbox{\textsf{toStr}($#1$)}}
\newcommand{\varn}{\mbox{$\mathbb{V}_{\mathbb{Z}}$}}
\newcommand{\vars}{\mbox{$\mathbb{V}_{\Sigma^*}$}}
\newcommand{\cvars}{\mbox{$\mathbb{V}_{\Sigma_\epsilon}$}}
\newcommand{\pvars}{\mbox{$\mathbb{V}_{\sharp}$}}
%\newcommand{\cvar}{\mbox{$V_{\Sigma_\epsilon}$}}
%\newcommand{\cvarone}{\mbox{$V_{\Sigma_\epsilon}$}}
%\newcommand{\cvartwo}{\mbox{$V'_{\Sigma_\epsilon}$}}
\newcommand{\cvarone}{V}
\newcommand{\cvartwo}{V'}
\newcommand{\cvar}{V}
\newcommand{\modelsof}[1]{[\![#1]\!]}
\newcommand{\true}{\mbox{$\mathsf{true}$}}
\newcommand{\false}{\mbox{$\mathsf{false}$}}
\newcommand{\enc}[1]{[\![#1]\!]}
%\newcommand{\parikhof}[1]{\mathit{Parikh}{(#1)}}
\newcommand{\parikhof}[1]{\mathbb{P}{(#1)}}
\newcommand{\parikhwof}[2]{|#1|_{#2}}
%\newcommand{\semof}[1]{||#1||}
\newcommand{\semof}[1]{\modelsof{#1}}
\newcommand{\decode}[1]{\mathit{decode_{#1}}}
%\newcommand{\parikhfof}[1]{\Phi_{\parikhof{#1}}}
\newcommand{\parikhfof}[1]{\Phi_{\mathbb{P}}(#1)} %shouldn't it be something that takes automaton as parameter and returns formula?
\newcommand{\pim}{I_{\#}}
%\newcommand{\syncop}{\Cap}
\newcommand{\syncop}{\times}
\newcommand{\syncof}[2]{#1 \syncop #2}
\newcommand{\syncfof}[2]{\Psi_{\syncof {#1} {#2}}}
\newcommand{\syncT}{T_\syncop}
\newcommand{\pvarsof}[1]{\#{#1}}
\newcommand{\pvar}{\pvarsof V}
\newcommand{\pvarone}{\pvarsof V}
\newcommand{\pvartwo}{\pvarsof {V'}}
\newcommand{\defeq}{::=}
\newcommand{\encode}[1]{\mathit{encode}_{#1}}
\newcommand{\eqwrt}[1]{=_{#1}}
\newcommand{\iequiv}{\equiv}
\newcommand{\restrict}[2]{#1_{#2}}
\newcommand{\underf}[2]{\mathit{under}_#1(#2)}
\newcommand{\paf}{\psi}

>>>>

\begin{abstract}
String-number conversion is an important class of constraint needed for the symbolic execution of string-manipulating programs. In particular solving string constraints with string-number conversion  is necessary  for the analysis of scripting languages such as JavaScript and Python, where string-number conversion is a part of the definition of the core semantics of these languages. However, the state-of-the-art constraint solvers have only very limited support to this type of constraint. To overcome these limitations, we propose, in this paper, an approach that can support a combination of string-number conversion as well as other common types of string constraints efficiently. Experimental results show that it significantly outperforms other state-of-the-art tools on benchmarks that involves string-number conversion.
\end{abstract}
 \setcopyright{none} 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{document}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\newcommand{\hide}[1]{}
\newcommand{\tool}{{\textsf{Z3-PFA}}}
\newcommand{\dr}{\mathcal{R}}
\newcommand{\nat}{\mathbb{N}}
\newcommand{\integers}{\mathbb{Z}}
\newcommand{\todo}[1]{{\color{blue}TODO: #1}}
\newcommand{\lh}[1]{{\color{orange}Lukas: #1}}
\newcommand{\changed}[1]{{\color{orange}#1}}
\newcommand{\yfc}[1]{{\color{blue}YFC: #1}}
\newcommand{\petr}[1]{{\color{pink}Petr: #1}}
\newcommand{\chatAt}[2]{\mbox{\textsf{charAt}($#1$, $#2$)}}
\newcommand{\ite}[3]{\mbox{\textsf{ite}($#1$, $#2$, $#3$)}}
\newcommand{\sti}[1]{\mbox{\textsf{toNum}($#1$)}}
\newcommand{\its}[1]{\mbox{\textsf{toStr}($#1$)}}
\newcommand{\varn}{\mbox{$\mathbb{V}_{\mathbb{Z}}$}}
\newcommand{\vars}{\mbox{$\mathbb{V}_{\Sigma^*}$}}
\newcommand{\cvars}{\mbox{$\mathbb{V}_{\Sigma_\epsilon}$}}
\newcommand{\pvars}{\mbox{$\mathbb{V}_{\sharp}$}}
%\newcommand{\cvar}{\mbox{$V_{\Sigma_\epsilon}$}}
%\newcommand{\cvarone}{\mbox{$V_{\Sigma_\epsilon}$}}
%\newcommand{\cvartwo}{\mbox{$V'_{\Sigma_\epsilon}$}}
\newcommand{\cvarone}{V}
\newcommand{\cvartwo}{V'}
\newcommand{\cvar}{V}
\newcommand{\modelsof}[1]{[\![#1]\!]}
\newcommand{\true}{\mbox{$\mathsf{true}$}}
\newcommand{\false}{\mbox{$\mathsf{false}$}}
\newcommand{\enc}[1]{[\![#1]\!]}
%\newcommand{\parikhof}[1]{\mathit{Parikh}{(#1)}}
\newcommand{\parikhof}[1]{\mathbb{P}{(#1)}}
\newcommand{\parikhwof}[2]{|#1|_{#2}}
%\newcommand{\semof}[1]{||#1||}
\newcommand{\semof}[1]{\modelsof{#1}}
\newcommand{\decode}[1]{\mathit{decode_{#1}}}
%\newcommand{\parikhfof}[1]{\Phi_{\parikhof{#1}}}
\newcommand{\parikhfof}[1]{\Phi_{\mathbb{P}}(#1)} %shouldn't it be something that takes automaton as parameter and returns formula?
\newcommand{\pim}{I_{\#}}
%\newcommand{\syncop}{\Cap}
\newcommand{\syncop}{\times}
\newcommand{\syncof}[2]{#1 \syncop #2}
\newcommand{\syncfof}[2]{\Psi_{\syncof {#1} {#2}}}
\newcommand{\syncT}{T_\syncop}
\newcommand{\pvarsof}[1]{\#{#1}}
\newcommand{\pvar}{\pvarsof V}
\newcommand{\pvarone}{\pvarsof V}
\newcommand{\pvartwo}{\pvarsof {V'}}
\newcommand{\defeq}{::=}
\newcommand{\encode}[1]{\mathit{encode}_{#1}}
\newcommand{\eqwrt}[1]{=_{#1}}
\newcommand{\iequiv}{\equiv}
\newcommand{\restrict}[2]{#1_{#2}}
\newcommand{\underf}[2]{\mathit{under}_#1(#2)}
\newcommand{\paf}{\psi}
